---
title: "Plots for Thesis"
author: "Vasiliki Gkika"
date: "2025-02-13"
output: pdf_document
---

# Set up

```{r}
setwd("C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/results_final/M200_v3")
library(ggplot2)
options(scipen = 999)

tt = seq(0, 200, by = 0.1)
nt = length(tt)
# event and censoring coefficients
lx = 0.05; beta = c(0.5, 0.8) # moderate dependency
```

# Scenario 1 

## True Curve

```{r}
integrand = function(t, z1, z2){
  exp(-lx * t * exp(beta[1]*z1 + beta[2]*z2)) * dnorm(z2)
}

true_surv_integr = numeric(nt)
for (i in 1:nt){
  true_surv_integr[i] = 0.5*(integrate(integrand, t = tt[i], z1 = 1, lower = -5, upper = 5)$value + 
                               integrate(integrand, t = tt[i], z1 = 0, lower = -5, upper = 5)$value)
}
```

```{r}
load("results_s1.Rdata")

s1_200_v3 = out_s1$`n = 200`
s1_500_v3 = out_s1$`n = 500`
s1_1000_v3 = out_s1$`n = 1000`
```

## Performance Metrics

```{r}
round(s1_200_v3$performance_metrics, digits = 4)
round(s1_500_v3$performance_metrics, digits = 4)
round(s1_1000_v3$performance_metrics, digits = 4)
```

## Plots

### I) GC

```{r}
png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/gc_n200_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 1: Correctly Specified Models (n = 200)")
lines(tt, s1_200_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s1_200_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s1_200_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation"),
       col = c("black", "red", "darkgreen", "blue"), 
       lwd = 2, lty = c(1, 2, 4, 3))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/gc_n500_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 1: Correctly Specified Models (n = 500)")
lines(tt, s1_500_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s1_500_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s1_500_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation"),
       col = c("black", "red", "darkgreen", "blue"), 
       lwd = 2, lty = c(1, 2, 4, 3))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/gc_n1000_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 1: Correctly Specified Models (n = 1000)")
lines(tt, s1_1000_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s1_1000_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s1_1000_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation"),
       col = c("black", "red", "darkgreen", "blue"), 
       lwd = 2, lty = c(1, 2, 4, 3))

dev.off()
```

### II) DR

```{r}
png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s1_n200_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 1: Correctly Specified Models (n = 200)")
lines(tt, s1_200_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s1_200_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s1_200_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s1_200_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s1_200_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s1_n500_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 1: Correctly Specified Models (n = 500)")
lines(tt, s1_500_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s1_500_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s1_500_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s1_500_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s1_500_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s1_n1000_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 1: Correctly Specified Models (n = 1000)")
lines(tt, s1_1000_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s1_1000_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s1_1000_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s1_1000_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s1_1000_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()
```

# Scenario 2

## True Curve

```{r}
integrand = function(t, z1, z2){
  exp(-0.03 * t * exp(beta[1]*z1 + beta[2]*z2)) * dnorm(z2)
}

true_surv_integr = numeric(nt)
for (i in 1:nt){
  true_surv_integr[i] = 0.5*(integrate(integrand, t = tt[i], z1 = 1, lower = -5, upper = 5)$value + 
                               integrate(integrand, t = tt[i], z1 = 0, lower = -5, upper = 5)$value)
}
```

```{r}
load("results_s2.Rdata")

s2_200_v3 = out_s2$`n = 200`
s2_500_v3 = out_s2$`n = 500`
s2_1000_v3 = out_s2$`n = 1000`
```

## Performance Metrics

```{r}
round(s2_200_v3$performance_metrics, digits = 4)
round(s2_500_v3$performance_metrics, digits = 4)
round(s2_1000_v3$performance_metrics, digits = 4)
```

## Plots

```{r}
png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/dr_s2_n200_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 2: Misspecify Censoring Model (n = 200)")
lines(tt, s2_200_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s2_200_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s2_200_v3$GC_curve, type = "s", col = "blue", lwd = 4, lty = 3)
lines(tt, s2_200_v3$DR_StabW, type = "s", col = "purple", lwd = 3, lty = 6)
lines(tt, s2_200_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/dr_s2_n500_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 2: Misspecify Censoring Model (n = 500)")
lines(tt, s2_500_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s2_500_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s2_500_v3$GC_curve, type = "s", col = "blue", lwd = 4, lty = 3)
lines(tt, s2_500_v3$DR_StabW, type = "s", col = "purple", lwd = 3, lty = 6)
lines(tt, s2_500_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/dr_s2_n1000_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 2: Misspecify Censoring Model (n = 1000)")
lines(tt, s2_1000_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s2_1000_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s2_1000_v3$GC_curve, type = "s", col = "blue", lwd = 4, lty = 3)
lines(tt, s2_1000_v3$DR_StabW, type = "s", col = "purple", lwd = 3, lty = 6)
lines(tt, s2_1000_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()
```

# Scenario 2b 

Run Scenario 2 for a second time. (WGC's metrics were increasing from n=500 to n=1000 in Scenario 2)

## True Curve

```{r}
integrand = function(t, z1, z2){
  exp(-0.03 * t * exp(beta[1]*z1 + beta[2]*z2)) * dnorm(z2)
}

true_surv_integr = numeric(nt)
for (i in 1:nt){
  true_surv_integr[i] = 0.5*(integrate(integrand, t = tt[i], z1 = 1, lower = -5, upper = 5)$value + 
                               integrate(integrand, t = tt[i], z1 = 0, lower = -5, upper = 5)$value)
}
```

```{r}
load("results_s2b.Rdata")

s2b_200_v3 = out_s2$`n = 200`
s2b_500_v3 = out_s2$`n = 500`
s2b_1000_v3 = out_s2$`n = 1000`
```

## Performance Metrics

```{r}
round(s2b_200_v3$performance_metrics, digits = 4)
round(s2b_500_v3$performance_metrics, digits = 4)
round(s2b_1000_v3$performance_metrics, digits = 4)
```

## Plots

```{r}
png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s2b_n200_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 2: Misspecify Censoring Model (n = 200)")
lines(tt, s2b_200_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s2b_200_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s2b_200_v3$GC_curve, type = "s", col = "blue", lwd = 4, lty = 3)
lines(tt, s2b_200_v3$DR_StabW, type = "s", col = "purple", lwd = 3, lty = 6)
lines(tt, s2b_200_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s2b_n500_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 2: Misspecify Censoring Model (n = 500)")
lines(tt, s2b_500_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s2b_500_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s2b_500_v3$GC_curve, type = "s", col = "blue", lwd = 4, lty = 3)
lines(tt, s2b_500_v3$DR_StabW, type = "s", col = "purple", lwd = 3, lty = 6)
lines(tt, s2b_500_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s2b_n1000_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 2: Misspecify Censoring Model (n = 1000)")
lines(tt, s2b_1000_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s2b_1000_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s2b_1000_v3$GC_curve, type = "s", col = "blue", lwd = 4, lty = 3)
lines(tt, s2b_1000_v3$DR_StabW, type = "s", col = "purple", lwd = 3, lty = 6)
lines(tt, s2b_1000_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()
```

# Scenario 3

## True Curve

```{r}
integrand = function(t, z1, z2){
  exp(-0.01 * t * exp(beta[1]*z1 + 1*I(z2^2))) * dnorm(z2)
}

true_surv_integr = numeric(nt)
for (i in 1:nt){
  true_surv_integr[i] = 0.5*(integrate(integrand, t = tt[i], z1 = 1, lower = -5, upper = 5)$value + 
                               integrate(integrand, t = tt[i], z1 = 0, lower = -5, upper = 5)$value)
}
```

```{r}
load("results_s3.Rdata")

s3_200_v3 = out_s3$`n = 200`
s3_500_v3 = out_s3$`n = 500`
s3_1000_v3 = out_s3$`n = 1000`
```

## Performance Metrics

```{r}
round(s3_200_v3$performance_metrics, digits = 4)
round(s3_500_v3$performance_metrics, digits = 4)
round(s3_1000_v3$performance_metrics, digits = 4)
```

## Plots

```{r}
png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/dr_s3_n200_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 3: Misspecify Outcome Model (n = 200)")
lines(tt, s3_200_v3$KM_curve, type = "s", col = "red", lwd = 3, lty = 2)
lines(tt, s3_200_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s3_200_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s3_200_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s3_200_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/dr_s3_n500_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 3: Misspecify Outcome Model (n = 500)")
lines(tt, s3_500_v3$KM_curve, type = "s", col = "red", lwd = 3, lty = 2)
lines(tt, s3_500_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s3_500_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s3_500_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s3_500_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/dr_s3_n1000_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 3, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 3: Misspecify Outcome Model (n = 1000)")
lines(tt, s3_1000_v3$KM_curve, type = "s", col = "red", lwd = 3, lty = 2)
lines(tt, s3_1000_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 2, lty = 4)
lines(tt, s3_1000_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s3_1000_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s3_1000_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()
```

# Scenario 4

## True Curve

```{r}
integrand = function(t, z1, z2){
  exp(-0.01 * t * exp(beta[1]*z1 + 1*I(z2^2))) * dnorm(z2)
}

true_surv_integr = numeric(nt)
for (i in 1:nt){
  true_surv_integr[i] = 0.5*(integrate(integrand, t = tt[i], z1 = 1, lower = -5, upper = 5)$value + 
                               integrate(integrand, t = tt[i], z1 = 0, lower = -5, upper = 5)$value)
}
```

```{r}
load("results_s4.Rdata")

s4_200_v3 = out_s4$`n = 200`
s4_500_v3 = out_s4$`n = 500`
s4_1000_v3 = out_s4$`n = 1000`
```

## Performance Metrics

```{r}
round(s4_200_v3$performance_metrics, digits = 4)
round(s4_500_v3$performance_metrics, digits = 4)
round(s4_1000_v3$performance_metrics, digits = 4)
```

## Plots

```{r}
png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s4a_n200_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 4a: Misspecify Both Models (n = 200)")
lines(tt, s4_200_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s4_200_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s4_200_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s4_200_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s4_200_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s4a_n500_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 4a: Misspecify Both Models (n = 500)")
lines(tt, s4_500_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s4_500_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s4_500_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s4_500_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s4_500_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s4a_n1000_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 4a: Misspecify Both Models (n = 1000)")
lines(tt, s4_1000_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s4_1000_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s4_1000_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s4_1000_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s4_1000_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()
```

# Scenario 4b

## True Curve

```{r}
integrand = function(t, z1, z2){
  exp(-0.01 * t * exp(beta[1]*z1 + 2*(z2 > 0))) * dnorm(z2)
}

true_surv_integr = numeric(nt)
for (i in 1:nt){
  true_surv_integr[i] = 0.5*(integrate(integrand, t = tt[i], z1 = 1, lower = -5, upper = 5)$value + 
                               integrate(integrand, t = tt[i], z1 = 0, lower = -5, upper = 5)$value)
}
```

```{r}
load("results_s4b.Rdata")

s4b_200_v3 = out_s4b$`n = 200`
s4b_500_v3 = out_s4b$`n = 500`
s4b_1000_v3 = out_s4b$`n = 1000`
```

## Performance Metrics

```{r}
round(s4b_200_v3$performance_metrics, digits = 4)
round(s4b_500_v3$performance_metrics, digits = 4)
round(s4b_1000_v3$performance_metrics, digits = 4)
```

## Plots

```{r}
png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s4b_n200_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 4b: Misspecify Both Models (n = 200)")
lines(tt, s4b_200_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s4b_200_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s4b_200_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s4b_200_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s4b_200_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s4b_n500_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 4b: Misspecify Both Models (n = 500)")
lines(tt, s4b_500_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s4b_500_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s4b_500_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s4b_500_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s4b_500_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()

png(file = "C:/Users/Vicky/Desktop/Vicky/Leiden/Leiden University/MSc Statistics & Data Science/5th Semester/Thesis/code/figures/v3/dr_s4b_n1000_v3.png", width = 7, height = 5, units = "in", res = 100)

plot(tt, true_surv_integr, type = "s", lwd = 2, bty = "l", las = 1,
     xlab = "Time", ylab = "Survival Probability",
     main = "Scenario 4b: Misspecify Both Models (n = 1000)")
lines(tt, s4b_1000_v3$KM_curve, type = "s", col = "red", lwd = 2, lty = 2)
lines(tt, s4b_1000_v3$IPCW_curve, type = "s", col = "darkgreen", lwd = 3, lty = 4)
lines(tt, s4b_1000_v3$GC_curve, type = "s", col = "blue", lwd = 3, lty = 3)
lines(tt, s4b_1000_v3$DR_StabW, type = "s", col = "purple", lwd = 2, lty = 6)
lines(tt, s4b_1000_v3$DR_WGC, type = "s", col = "orange", lwd = 2, lty = 2)

legend("topright", title = "Survival Curves", bty = "n", 
       c("True theoretical", "Kaplan-Meier", 
         "IPCW", "G-Computation", 
         "AIPCW", "WGC"),
       col = c("black", "red", "darkgreen", "blue", "purple", "orange"), 
       lwd = 2, lty = c(1, 2, 4, 3, 6, 2))

dev.off()
```

# Final aggregated comparisons

## S1

```{r}
metrics_s1_bias = data.frame('Value' = c(t(s1_200_v3$performance_metrics[1, ]), 
                                    t(s1_500_v3$performance_metrics[1, ]),
                                    t(s1_1000_v3$performance_metrics[1, ])),
                         'Method' = c(rownames(t(s1_200_v3$performance_metrics[1, ])),
                                      rownames(t(s1_500_v3$performance_metrics[1, ])),
                                      rownames(t(s1_1000_v3$performance_metrics[1, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Absolute Bias", 15))
metrics_s1_var = data.frame('Value' = c(t(s1_200_v3$performance_metrics[2, ]), 
                                    t(s1_500_v3$performance_metrics[2, ]),
                                    t(s1_1000_v3$performance_metrics[2, ])),
                         'Method' = c(rownames(t(s1_200_v3$performance_metrics[2, ])),
                                      rownames(t(s1_500_v3$performance_metrics[2, ])),
                                      rownames(t(s1_1000_v3$performance_metrics[2, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("RMSE", 15))
metrics_s1_rmse = data.frame('Value' = c(t(s1_200_v3$performance_metrics[3, ]), 
                                    t(s1_500_v3$performance_metrics[3, ]),
                                    t(s1_1000_v3$performance_metrics[3, ])),
                         'Method' = c(rownames(t(s1_200_v3$performance_metrics[3, ])),
                                      rownames(t(s1_500_v3$performance_metrics[3, ])),
                                      rownames(t(s1_1000_v3$performance_metrics[3, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Area Between the Curves", 15))
metrics_s1_area = data.frame('Value' = c(t(s1_200_v3$performance_metrics[4, ]), 
                                    t(s1_500_v3$performance_metrics[4, ]),
                                    t(s1_1000_v3$performance_metrics[4, ])),
                         'Method' = c(rownames(t(s1_200_v3$performance_metrics[4, ])),
                                      rownames(t(s1_500_v3$performance_metrics[4, ])),
                                      rownames(t(s1_1000_v3$performance_metrics[4, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Variance", 15))

metrics_s1 = rbind(metrics_s1_bias, metrics_s1_var, metrics_s1_rmse, metrics_s1_area)

metrics_s1$n = as.factor(metrics_s1$n)
metrics_s1$Method = factor(metrics_s1$Method, levels = c("KM", "IPCW", "G-C", "DR_StabW", "DR_WGC"),
                                              labels = c("KM", "IPCW", "GC", "AIPCW", "WGC"))
metrics_s1$Metric = as.factor(metrics_s1$Metric)
```

### I) GC

```{r}
ggplot(data = metrics_s1[-which(metrics_s1$Method %in% c("AIPCW", "WGC")), ], aes(x = n, y = Value, col = Method, shape = Method)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.3)) + 
    facet_wrap(vars(Metric), scales = "free", dir = "v") +
    scale_shape_manual(values = c(15, 16, 18, 17, 8)) +
    scale_color_manual(values = c("#F8766D", "#00BA38", "#619CFF", "#A835D1", "#F79C5E")) +
    xlab("Sample size (n)") +
    ylab(NULL) +
    ggtitle("Scenario 1: Correctly Specified Models") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_line(color = "lightgrey", linewidth = 0.3),
          axis.ticks = element_line(color = "black"),
          strip.background = element_rect(fill = "lightgrey", color = "lightgrey"))
```

### II) DR

```{r}
ggplot(data = metrics_s1, aes(x = n, y = Value, col = Method, shape = Method)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.3)) + 
    facet_wrap(vars(Metric), scales = "free", dir = "v") +
    scale_shape_manual(values = c(15, 16, 18, 17, 8)) +
    scale_color_manual(values = c("#F8766D", "#00BA38", "#619CFF", "#A835D1", "#F79C5E")) +
    xlab("Sample size (n)") +
    ylab(NULL) +
    ggtitle("Scenario 1: Correctly Specified Models") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_line(color = "lightgrey", linewidth = 0.3),
          axis.ticks = element_line(color = "black"),
          strip.background = element_rect(fill = "lightgrey", color = "lightgrey"))
```

## S2

```{r}
metrics_s2_bias = data.frame('Value' = c(t(s2b_200_v3$performance_metrics[1, ]), 
                                    t(s2b_500_v3$performance_metrics[1, ]),
                                    t(s2b_1000_v3$performance_metrics[1, ])),
                         'Method' = c(rownames(t(s2b_200_v3$performance_metrics[1, ])),
                                      rownames(t(s2b_500_v3$performance_metrics[1, ])),
                                      rownames(t(s2b_1000_v3$performance_metrics[1, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Absolute Bias", 15))
metrics_s2_var = data.frame('Value' = c(t(s2b_200_v3$performance_metrics[2, ]), 
                                    t(s2b_500_v3$performance_metrics[2, ]),
                                    t(s2b_1000_v3$performance_metrics[2, ])),
                         'Method' = c(rownames(t(s2b_200_v3$performance_metrics[2, ])),
                                      rownames(t(s2b_500_v3$performance_metrics[2, ])),
                                      rownames(t(s2b_1000_v3$performance_metrics[2, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("RMSE", 15))
metrics_s2_rmse = data.frame('Value' = c(t(s2b_200_v3$performance_metrics[3, ]), 
                                    t(s2b_500_v3$performance_metrics[3, ]),
                                    t(s2b_1000_v3$performance_metrics[3, ])),
                         'Method' = c(rownames(t(s2b_200_v3$performance_metrics[3, ])),
                                      rownames(t(s2b_500_v3$performance_metrics[3, ])),
                                      rownames(t(s2b_1000_v3$performance_metrics[3, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Area Between the Curves", 15))
metrics_s2_area = data.frame('Value' = c(t(s2b_200_v3$performance_metrics[4, ]), 
                                    t(s2b_500_v3$performance_metrics[4, ]),
                                    t(s2b_1000_v3$performance_metrics[4, ])),
                         'Method' = c(rownames(t(s2b_200_v3$performance_metrics[4, ])),
                                      rownames(t(s2b_500_v3$performance_metrics[4, ])),
                                      rownames(t(s2b_1000_v3$performance_metrics[4, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Variance", 15))

metrics_s2 = rbind(metrics_s2_bias, metrics_s2_var, metrics_s2_rmse, metrics_s2_area)

metrics_s2$n = as.factor(metrics_s2$n)
metrics_s2$Method = factor(metrics_s2$Method, levels = c("KM", "IPCW", "G-C", "DR_StabW", "DR_WGC"),
                                              labels = c("KM", "IPCW", "GC", "AIPCW", "WGC"))
metrics_s2$Metric = as.factor(metrics_s2$Metric)
```

```{r}
ggplot(data = metrics_s2, aes(x = n, y = Value, col = Method, shape = Method)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.3)) + 
    facet_wrap(vars(Metric), scales = "free", dir = "v") +
    scale_shape_manual(values = c(15, 16, 18, 17, 8)) +
    scale_color_manual(values = c("#F8766D", "#00BA38", "#619CFF", "#A835D1", "#F79C5E")) +
    xlab("Sample size (n)") +
    ylab(NULL) +
    ggtitle("Scenario 2: Misspecify Censoring Model") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_line(color = "lightgrey", linewidth = 0.3),
          axis.ticks = element_line(color = "black"),
          strip.background = element_rect(fill = "lightgrey", color = "lightgrey"))
```

## S3

```{r}
metrics_s3_bias = data.frame('Value' = c(t(s3_200_v3$performance_metrics[1, ]), 
                                    t(s3_500_v3$performance_metrics[1, ]),
                                    t(s3_1000_v3$performance_metrics[1, ])),
                         'Method' = c(rownames(t(s3_200_v3$performance_metrics[1, ])),
                                      rownames(t(s3_500_v3$performance_metrics[1, ])),
                                      rownames(t(s3_1000_v3$performance_metrics[1, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Absolute Bias", 15))
metrics_s3_var = data.frame('Value' = c(t(s3_200_v3$performance_metrics[2, ]), 
                                    t(s3_500_v3$performance_metrics[2, ]),
                                    t(s3_1000_v3$performance_metrics[2, ])),
                         'Method' = c(rownames(t(s3_200_v3$performance_metrics[2, ])),
                                      rownames(t(s3_500_v3$performance_metrics[2, ])),
                                      rownames(t(s3_1000_v3$performance_metrics[2, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("RMSE", 15))
metrics_s3_rmse = data.frame('Value' = c(t(s3_200_v3$performance_metrics[3, ]), 
                                    t(s3_500_v3$performance_metrics[3, ]),
                                    t(s3_1000_v3$performance_metrics[3, ])),
                         'Method' = c(rownames(t(s3_200_v3$performance_metrics[3, ])),
                                      rownames(t(s3_500_v3$performance_metrics[3, ])),
                                      rownames(t(s3_1000_v3$performance_metrics[3, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Area Between the Curves", 15))
metrics_s3_area = data.frame('Value' = c(t(s3_200_v3$performance_metrics[4, ]), 
                                    t(s3_500_v3$performance_metrics[4, ]),
                                    t(s3_1000_v3$performance_metrics[4, ])),
                         'Method' = c(rownames(t(s3_200_v3$performance_metrics[4, ])),
                                      rownames(t(s3_500_v3$performance_metrics[4, ])),
                                      rownames(t(s3_1000_v3$performance_metrics[4, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Variance", 15))

metrics_s3 = rbind(metrics_s3_bias, metrics_s3_var, metrics_s3_rmse, metrics_s3_area)

metrics_s3$n = as.factor(metrics_s3$n)
metrics_s3$Method = factor(metrics_s3$Method, levels = c("KM", "IPCW", "G-C", "DR_StabW", "DR_WGC"),
                                              labels = c("KM", "IPCW", "GC", "AIPCW", "WGC"))
metrics_s3$Metric = as.factor(metrics_s3$Metric)
```

```{r}
ggplot(data = metrics_s3, aes(x = n, y = Value, col = Method, shape = Method)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.3)) + 
    facet_wrap(vars(Metric), scales = "free", dir = "v") +
    scale_shape_manual(values = c(15, 16, 18, 17, 8)) +
    scale_color_manual(values = c("#F8766D", "#00BA38", "#619CFF", "#A835D1", "#F79C5E")) +
    xlab("Sample size (n)") +
    ylab(NULL) +
    ggtitle("Scenario 3: Misspecify Outcome Model") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_line(color = "lightgrey", linewidth = 0.3),
          axis.ticks = element_line(color = "black"),
          strip.background = element_rect(fill = "lightgrey", color = "lightgrey"))
```

## S4

```{r}
metrics_s4_bias = data.frame('Value' = c(t(s4_200_v3$performance_metrics[1, ]), 
                                    t(s4_500_v3$performance_metrics[1, ]),
                                    t(s4_1000_v3$performance_metrics[1, ])),
                         'Method' = c(rownames(t(s4_200_v3$performance_metrics[1, ])),
                                      rownames(t(s4_500_v3$performance_metrics[1, ])),
                                      rownames(t(s4_1000_v3$performance_metrics[1, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Absolute Bias", 15))
metrics_s4_var = data.frame('Value' = c(t(s4_200_v3$performance_metrics[2, ]), 
                                    t(s4_500_v3$performance_metrics[2, ]),
                                    t(s4_1000_v3$performance_metrics[2, ])),
                         'Method' = c(rownames(t(s4_200_v3$performance_metrics[2, ])),
                                      rownames(t(s4_500_v3$performance_metrics[2, ])),
                                      rownames(t(s4_1000_v3$performance_metrics[2, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("RMSE", 15))
metrics_s4_rmse = data.frame('Value' = c(t(s4_200_v3$performance_metrics[3, ]), 
                                    t(s4_500_v3$performance_metrics[3, ]),
                                    t(s4_1000_v3$performance_metrics[3, ])),
                         'Method' = c(rownames(t(s4_200_v3$performance_metrics[3, ])),
                                      rownames(t(s4_500_v3$performance_metrics[3, ])),
                                      rownames(t(s4_1000_v3$performance_metrics[3, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Area Between the Curves", 15))
metrics_s4_area = data.frame('Value' = c(t(s4_200_v3$performance_metrics[4, ]), 
                                    t(s4_500_v3$performance_metrics[4, ]),
                                    t(s4_1000_v3$performance_metrics[4, ])),
                         'Method' = c(rownames(t(s4_200_v3$performance_metrics[4, ])),
                                      rownames(t(s4_500_v3$performance_metrics[4, ])),
                                      rownames(t(s4_1000_v3$performance_metrics[4, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Variance", 15))

metrics_s4 = rbind(metrics_s4_bias, metrics_s4_var, metrics_s4_rmse, metrics_s4_area)

metrics_s4$n = as.factor(metrics_s4$n)
metrics_s4$Method = factor(metrics_s4$Method, levels = c("KM", "IPCW", "G-C", "DR_StabW", "DR_WGC"),
                                              labels = c("KM", "IPCW", "GC", "AIPCW", "WGC"))
metrics_s4$Metric = as.factor(metrics_s4$Metric)
```

```{r}
ggplot(data = metrics_s4, aes(x = n, y = Value, col = Method, shape = Method)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.3)) + 
    facet_wrap(vars(Metric), scales = "free", dir = "v") +
    scale_shape_manual(values = c(15, 16, 18, 17, 8)) +
    scale_color_manual(values = c("#F8766D", "#00BA38", "#619CFF", "#A835D1", "#F79C5E")) +
    xlab("Sample size (n)") +
    ylab(NULL) +
    ggtitle("Scenario 4a: Misspecify Both Models") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_line(color = "lightgrey", linewidth = 0.3),
          axis.ticks = element_line(color = "black"),
          strip.background = element_rect(fill = "lightgrey", color = "lightgrey"))
```

## S4b

```{r}
metrics_s4b_bias = data.frame('Value' = c(t(s4b_200_v3$performance_metrics[1, ]), 
                                    t(s4b_500_v3$performance_metrics[1, ]),
                                    t(s4b_1000_v3$performance_metrics[1, ])),
                         'Method' = c(rownames(t(s4b_200_v3$performance_metrics[1, ])),
                                      rownames(t(s4b_500_v3$performance_metrics[1, ])),
                                      rownames(t(s4b_1000_v3$performance_metrics[1, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Absolute Bias", 15))
metrics_s4b_var = data.frame('Value' = c(t(s4b_200_v3$performance_metrics[2, ]), 
                                    t(s4b_500_v3$performance_metrics[2, ]),
                                    t(s4b_1000_v3$performance_metrics[2, ])),
                         'Method' = c(rownames(t(s4b_200_v3$performance_metrics[2, ])),
                                      rownames(t(s4b_500_v3$performance_metrics[2, ])),
                                      rownames(t(s4b_1000_v3$performance_metrics[2, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("RMSE", 15))
metrics_s4b_rmse = data.frame('Value' = c(t(s4b_200_v3$performance_metrics[3, ]), 
                                    t(s4b_500_v3$performance_metrics[3, ]),
                                    t(s4b_1000_v3$performance_metrics[3, ])),
                         'Method' = c(rownames(t(s4b_200_v3$performance_metrics[3, ])),
                                      rownames(t(s4b_500_v3$performance_metrics[3, ])),
                                      rownames(t(s4b_1000_v3$performance_metrics[3, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Area Between the Curves", 15))
metrics_s4b_area = data.frame('Value' = c(t(s4b_200_v3$performance_metrics[4, ]), 
                                    t(s4b_500_v3$performance_metrics[4, ]),
                                    t(s4b_1000_v3$performance_metrics[4, ])),
                         'Method' = c(rownames(t(s4b_200_v3$performance_metrics[4, ])),
                                      rownames(t(s4b_500_v3$performance_metrics[4, ])),
                                      rownames(t(s4b_1000_v3$performance_metrics[4, ]))),
                         'n' = c(rep(200, 5),
                                 rep(500, 5),
                                 rep(1000, 5)),
                         'Metric' = rep("Variance", 15))

metrics_s4b = rbind(metrics_s4b_bias, metrics_s4b_var, metrics_s4b_rmse, metrics_s4b_area)

metrics_s4b$n = as.factor(metrics_s4b$n)
metrics_s4b$Method = factor(metrics_s4b$Method, levels = c("KM", "IPCW", "G-C", "DR_StabW", "DR_WGC"),
                                              labels = c("KM", "IPCW", "GC", "AIPCW", "WGC"))
metrics_s4b$Metric = as.factor(metrics_s4b$Metric)
```

```{r}
ggplot(data = metrics_s4b, aes(x = n, y = Value, col = Method, shape = Method)) +
    geom_point(size = 2.5, position = position_dodge(width = 0.3)) + 
    facet_wrap(vars(Metric), scales = "free", dir = "v") +
    scale_shape_manual(values = c(15, 16, 18, 17, 8)) +
    scale_color_manual(values = c("#F8766D", "#00BA38", "#619CFF", "#A835D1", "#F79C5E")) +
    xlab("Sample size (n)") +
    ylab(NULL) +
    ggtitle("Scenario 4b: Misspecify Both Models") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_line(color = "lightgrey", linewidth = 0.3),
          axis.ticks = element_line(color = "black"),
          strip.background = element_rect(fill = "lightgrey", color = "lightgrey"))
```









